Stack Safety as a Security Property

### 2020-07-09 main.tex
Nit: missing word in abstract

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
What is stack safety? Numerous mechanisms have been proposed to guard
against attacks that corrupt the call stacks of running programs, and many
others rely on a protected stack as an assumption to provide higher level
guarantees\bcp{this is a good point, but we don't pick it up anywhere in the
  paper, do we?}, a clear and precise definition of stack safety is missing
from the literature.

>>>>

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
What is stack safety? Numerous mechanisms have been proposed to guard
against attacks that corrupt the call stacks of running programs, and many
others rely on a protected stack as an assumption to provide higher level
guarantees\bcp{this is a good point, but we don't pick it up anywhere in the
  paper, do we?}, but a clear and precise definition of stack safety is missing
from the literature.
